Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-05-28 sources/bmc_template_submission/bmc_article.tex
some moretiny edits

\section*{Conclusions}
Data repositories hold more information than meets the eye.
Beyond the main data, they are rich sources of metadata that can be leveraged
for the advantage of all areas of biology as well as the advancement of scientific
policy, applications and education.
Scientific understanding is constantly challenged and reframed by new data and analyses.
Physcraper provides a framework for reproducible phylogenetics that has the
potential to consistently contextualize new knowledge in the light of previous understanding,
showcasing the utility and importance of good data sharing practices and open science for phylogenetics, biology and science.

>>>>

\section*{Conclusions}
Data repositories hold more information than meets the eye.
Beyond the main data, they are rich sources of metadata that can be leveraged
for the advantage of all areas of biology as well as the advancement of scientific
policy, applications and education.
Scientific understanding is constantly challenged and reframed by new data and analyses.
Physcraper provides a framework for reproducible phylogenetics that has the
potential to consistently contextualize new knowledge in the light of previous understanding,
showcasing the utility and importance of good data sharing practices and open research for phylogenetics, biology and science.
